Sparse Function-space Representation \\ of Neural Networks

### 2023-05-22 paper/main.tex
removed name from import
update appendix cl

For our method, DER, EWC, and SI, we relied on the Mammoth framework proposed by \citep{buzzega2020dark}, while we used the available open-source codebases to conduct the experiments respectively for FROMP, S-FSVI, and VCL.

@@

%% Hyperparms used in the different experiments:
\textbf{S-MNIST (40 pts./task):}
\begin{itemize}
	\item[-] Online-EWC: SGD with learning rate $0.03$, batch size  10, number of epochs 1, $\lambda=90$, $\gamma=1.0$.
	\item[-] SI: SGD with learning rate 0.1, batch size 10, number of epochs 1, $c=1.0$, $\xi=0.9$.
	\item[-] VCL (with coresets): Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
	\item[-] DER: SGD with learning rate 0.03, batch size 10, buffer batch size 10, number epochs 1, $\alpha=0.3$, reservoir buffer size 200.
	\item[-] FROMP: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$, random selection for memorable points.
	\item[-] S-FSVI: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 10.
	\item[-] SFR: Adam with learning rate 0.0003, batch size=32, $\tau=1$, $\delta=0.0001$,  number of epochs 1.
\end{itemize}

\textbf{S-MNIST (200 pts./task):}
\begin{itemize}
	\item[-] Online-EWC: SGD with learning rate $0.03$, batch size  10, number of epochs 1, $\lambda=90$, $\gamma=1.0$.
	\item[-] SI: SGD with learning rate 0.1, batch size 10, number of epochs 1, $c=1.0$, $\xi=0.9$.
	\item[-] VCL (with coresets): Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
	\item[-] DER: SGD with learning rate 0.03, batch size 10, buffer batch size 10, number epochs 1, $\alpha$ 0.2, reservoir buffer size 1000.
	\item[-] FROMP: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$, random selection for memorable points.
	\item[-] S-FSVI: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 80.
	\item[-] SFR: Adam learning rate 0.0001, batch size=32, $\tau=0.5$, $\delta=1 \cdot 10^{-5}$, number of epochs=5.
\end{itemize}

%% Placeholders for now
\textbf{S-FMNIST (200 pts./task):}
\begin{itemize}
	\item[-] Online-EWC: SGD with learning rate $0.03$, batch size  10, number of epochs 5, $\lambda=90$, $\gamma=1.0$.
	\item[-] SI: SGD with learning rate 0.1, batch size 10, number of epochs 5, $c=1.0$, $\xi=0.9$.
	\item[-] VCL (with coresets): Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
	\item[-] DER: SGD with learning rate 0.03, batch size 10, buffer batch size 10, number epochs 5, $\alpha$ 0.2, reservoir buffer size 200.
	\item[-] FROMP: Adam with learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$, random selection for memorable points.
	\item[-] S-FSVI: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 60.
	\item[-] SFR: Adam, learning rate=0.0003, batch size=32, $\tau=1.0$, $\delta=0.0001$, number of epochs=5.
\end{itemize}

\textbf{P-MNIST (200 pts./task):}
\begin{itemize}
	\item[-] Online-EWC: SGD with learning rate $0.1$, batch size 128, number of epochs 10, $\lambda=0.7$, $\gamma=1.0$.
	\item[-] SI: SGD with learning rate 0.1, batch size 138, number of epochs 10, $c=0.5$, $\xi=1.0$. 
	\item[-] VCL (with coresets): Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
	\item[-] DER:  SGD with learning rate 0.01, batch size 128, buffer batch size 128, number epochs 10, $\alpha=0.3$, reservoir buffer size 2000.
	\item[-] FROMP: Adam with learning rate $1 \cdot 10^{-3}$, batch size 128, number of epochs 10, $\tau = 0.5$, lambda descend selection for memorable points.
	\item[-] S-FSVI: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 10.
	\item[-] SFR: Adam learning 0.0003, batch size=64, $\tau=1.0$, $\delta=0.0001$. 
\end{itemize}

>>>>

For our method, DER, Online-EWC, and SI, we relied on the Mammoth framework proposed by \citep{buzzega2020dark}. On the other hand, we used the available open-source FROMP codebase to conduct the experiments with FROMP, and the S-FSVI codebase to run the experiments on S-FSVI and VCL. We selected the hyperparameters to use with all these methods trying to adapt the ones pointed out in the their original papers. For this reason, we relied on SGD for DER, Online-EWC, and SI, which requires higher learning rates, compared to the others methods for which we used Adam, \ie, our \our regularizer, FROMP, S-FSVI and VCL.

@@

%% Hyperparms used in the different experiments:
\textbf{S-MNIST (40 pts./task):}
\begin{itemize}
	\item[-] Online-EWC: SGD, learning rate $0.03$, batch size  10, number of epochs 1, $\lambda=90$, $\gamma=1.0$.
	\item[-] SI: SGD, learning rate 0.1, batch size 10, number of epochs 1, $c=1.0$, $\xi=0.9$.
	\item[-] VCL (with coresets): Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
	\item[-] DER: SGD with learning rate 0.03, batch size 10, buffer batch size 10, number epochs 1, $\alpha=0.3$, reservoir buffer size 200.
	\item[-] FROMP: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$, random selection for memorable points.
	\item[-] S-FSVI: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 10.
	\item[-] SFR: Adam, learning rate $3 \cdot 10^{-4}$, batch size 32, $\tau=1$, $\delta=0.0001$,  number of epochs 1.
\end{itemize}

\textbf{S-MNIST (200 pts./task):}
\begin{itemize}
	\item[-] Online-EWC: SGD, learning rate $0.03$, batch size  10, number of epochs 1, $\lambda=90$, $\gamma=1.0$.
	\item[-] SI: SGD, learning rate 0.1, batch size 10, number of epochs 1, $c=1.0$, $\xi=0.9$.
	\item[-] VCL (with coresets): Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
	\item[-] DER: SGD, learning rate 0.03, batch size 10, buffer batch size 10, number epochs 1, $\alpha$ 0.2, reservoir buffer size 1000.
	\item[-] FROMP: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$, random selection for memorable points.
	\item[-] S-FSVI: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 80.
	\item[-] SFR: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, $\tau=0.5$, $\delta=1 \cdot 10^{-5}$, number of epochs=5.
\end{itemize}

%% Placeholders for now
\textbf{S-FMNIST (200 pts./task):}
\begin{itemize}
	\item[-] Online-EWC: SGD, learning rate $0.03$, batch size  10, number of epochs 5, $\lambda=90$, $\gamma=1.0$.
	\item[-] SI: SGD, learning rate 0.1, batch size 10, number of epochs 5, $c=1.0$, $\xi=0.9$.
	\item[-] VCL (with coresets): Adam, learning rate $1 \cdot 10^{-3}$, batch size 256, number of epochs 100, selection method for coresets random choice.
	\item[-] DER: SGD, learning rate 0.03, batch size 10, buffer batch size 10, number epochs 5, $\alpha$ 0.2, reservoir buffer size 200.
	\item[-] FROMP: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$, random selection for memorable points.
	\item[-] S-FSVI: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 60.
	\item[-] SFR: Adam, learning rate $3 \cdot 10^{-4}$, batch size 32, $\tau=1.0$, $\delta=0.0001$, number of epochs=5.
\end{itemize}

\textbf{P-MNIST (200 pts./task):}
\begin{itemize}
	\item[-] Online-EWC: SGD, learning rate $0.1$, batch size 128, number of epochs 10, $\lambda=0.7$, $\gamma=1.0$.
	\item[-] SI: SGD, learning rate 0.1, batch size 138, number of epochs 10, $c=0.5$, $\xi=1.0$. 
	\item[-] VCL (with coresets): Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
	\item[-] DER:  SGD, learning rate 0.01, batch size 128, buffer batch size 128, number epochs 10, $\alpha=0.3$, reservoir buffer size 2000.
	\item[-] FROMP: Adam, learning rate $1 \cdot 10^{-3}$, batch size 128, number of epochs 10, $\tau = 0.5$, lambda descend selection for memorable points.
	\item[-] S-FSVI: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 10.
	\item[-] SFR: Adam, learning rate $3 \cdot 10^{-4}$, batch size 64, $\tau=1.0$, $\delta=0.0001$. 
\end{itemize}
